---
title: "Reproducible Research: Peer Assessment 2"
output: 
  html_document:
    keep_md: true
---
## Data Processing
We begin by loading libraries and setting a few global parameters:
```{r chunckGlobalOpts}
  library(knitr)
  opts_chunk$set(echo=TRUE, cache=TRUE)
  setwd("~/datasciencecoursera/RepResProj2/")
```

We first download and unzip the data (if necessary):
```{r chunkCheckFile}
  #Download file if it does not exist
  if (!file.exists("exdata-data-NEI_data.zip")) {
      message("Downloading data...")
      fileURL <- "http://goo.gl/FWZqTP"
      zipfile = "exdata-data-NEI_data.zip"
      download.file(fileURL, destfile=zipfile, method="curl")
      unzip(zipfile)
  }
```

We then read the data into R
```{r chunkReadData}
  # Load the csv files and assign it to a variable
  NEI   = readRDS("summarySCC_PM25.rds")
  SCC   = readRDS("Source_Classification_Code.rds")
```

The data contains
```{r}
  str(NEI)
```

## PLOT 1

### The Question
Have total emissions from PM2.5 decreased in the United States from 1999 to 2008? Using the base plotting system, make a plot showing the total $\sf{PM_{2.5}}$ emission from all sources for each of the years 1999, 2002, 2005, and 2008.

### The Analysis
```{r}
  hist(NEI$year)
```

```{r}
  ## Plot historgram and save PNG
  names(NEI)

```

```{r}
  ## Plot historgram and save PNG
  png("plot1.png", width = 480, height = 480)
  #plot
  dev.off()

```

## System Info
```{r}
sessionInfo()
```